r5r: Rapid Realistic Routing with R5 in R

### 2020-08-23 r-package/paper2020/paper2020.Rmd
updates do paper2020.Rmd draft intro

Transport routing is a fundamental step for the transport modeling required in 
accessibility analysis, fleet allocation and transport simulation and planning 
more broadly.

context that researcher and practitioners face practical challenges in transport routing
and accessibility analysis.
- licensed software
- time consuming compuations particularly for large and complex transport
mulimodal networks
- most options available only focus on fastest route, whach overlooks...

>>>>

Transport routing is the process of finding the alternative routes and costs 
that connect places on a given transport network. Routing often involves complex
mathematical algorithms and it is a fundamental step required for transport
accessibility analysis, fleet allocation and transport simulation and planning
more broadly.

Despite the long standing importance of routing analysis to the field, transport 
researchers and practitioners still frequently face practical challenges with 
this task. These challenges involve for example the monetary costs of licensed 
software, data availability issues for data hungry models, and the long 
computation times to run multiple routing scenarios, particularly in large and 
complex multimodal transport networks. While there is a growing number of open source routing models (ref: stplnr, otp, dodgr), most options available only return the fastest route, what overlooks....
